---
title: "Homework1-1"
author: "JinDian"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## 1

 The Iowa data set iowa.csv is a toy example that summarises the yield of wheat (bushels per acre) for
 the state of Iowa between 1930-1962. In addition to yield, year, rainfall and temperature were recorded
 as the main predictors of yield.
 a. First, we need to load the data set into R using the command read.csv(). Use the help function
 to learn what arguments this function takes. Once you have the necessary input, load the data
 set into R and make it a data frame called iowa.df.
 
 b. How many rows and columns does iowa.df have?
 
 c. What are the names of the columns of iowa.df?
 
 d. What is the value of row 5, column 7 of iowa.df?
 
 e. Display the second row of iowa.df in its entirety

```{r}
iowa.df <- read.csv("data/iowa.csv",header=T,sep = ";")
iowa.df
```
b.33 rows,10 columns.

c.Year,Rain0,Temp1,Rain1,Temp2,Rain2,Temp3,Rain3,Temp4,Yield.

d.the value of row 5,column 7 of iowa.df is `r iowa.df[5,7]`.

e.
```{r}
iowa.df[2,]
```

