---
title: "Homework1"
author: "JinDian"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## 1

### The Iowa data set iowa.csv is a toy example that summarises the yield of wheat (bushels per acre) for the state of Iowa between 1930-1962. In addition to yield, year, rainfall and temperature were recorded as the main predictors of yield.
 a. First, we need to load the data set into R using the command read.csv(). Use the help function
 to learn what arguments this function takes. Once you have the necessary input, load the data
 set into R and make it a data frame called iowa.df.
 
 b. How many rows and columns does iowa.df have?
 
 c. What are the names of the columns of iowa.df?
 
 d. What is the value of row 5, column 7 of iowa.df?
 
 e. Display the second row of iowa.df in its entirety

```{r}
iowa.df <- read.csv("data/iowa.csv",header=T,sep = ";")
iowa.df
```
b.33 rows,10 columns.

c.Year,Rain0,Temp1,Rain1,Temp2,Rain2,Temp3,Rain3,Temp4,Yield.

d.the value of row 5,column 7 of iowa.df is `r iowa.df[5,7]`.

e.
```{r}
iowa.df[2,]
```

## 2

### a. For each of the following commands, either explain why they should be errors, or explain the non-erroneous result.
 vector1 <- c("5", "12", "7", "32")
 max(vector1)
 sort(vector1)
 sum(vector1)
 
 1.vector1是一个由字符"5"  "12" "7"  "32"组成的向量
 
```{r}
vector1 <- c("5", "12", "7", "32")
vector1
```
2.max()函数输出最大值，由于vector1向量中都是字符，字符从左开始比较字符大小，分别比较5,1,7,3.显然最大的是"7"

```{r}
max(vector1)
```
3.sort()函数默认对vector1向量进行递增排序，根据字符大小比较的规则，从小到大依次是"12" "32" "5"  "7" 。

```{r}
sort(vector1)
```
4.出现error,因为vector1向量全是字符类型，无法进行sum().


### b. For the next series of commands, either explain their results, or why they should produce errors.
 vector2 <- c("5",7,12)
 vector2[2] + vector2[3]
 dataframe3 <- data.frame(z1="5",z2=7,z3=12)
 dataframe3[1,2] + dataframe3[1,3]
 list4 <- list(z1="6", z2=42, z3="49", z4=126)
 list4[[2]]+list4[[4]]
 list4[2]+list4[4]
 
1.向量必须包含同一种类型的元素，这里由于同时包含字符和数字类型数据，所以会把数字类型元素变成字符类型元素

```{r}
vector2 <- c("5",7,12)
vector2
```
 会出现error:二进列运算符中有非数值参数.原因是在给vector2赋值时，其第二个和第三个元素都变成了字符类型数据，所以不能进行加运算

2.
```{r}
dataframe3 <- data.frame(z1="5",z2=7,z3=12)
dataframe3
```
```{r}
dataframe3[1,2] + dataframe3[1,3]
```
dataframe3是dataframe类型的数据，它的nrow=1,dataframe3[1,2] =7,dataframe3[1,3]=12，两个数加起来是19.

3.

list4是lists类型数据，list4[[2]]和list4[[4]]分别表示list4的第2个和第4个元素，二者都是数字类型，可以进行相加计算.list4[2]和list4[4]分别表示只包含第2个和第4个元素的新list，两个list不能直接进行相加运算。
