---
title: "Homework1"
author: "JinDian"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 1

### The Iowa data set iowa.csv is a toy example that summarises the yield of wheat (bushels per acre) for the state of Iowa between 1930-1962. In addition to yield, year, rainfall and temperature were recorded as the main predictors of yield.
 a. First, we need to load the data set into R using the command read.csv(). Use the help function
 to learn what arguments this function takes. Once you have the necessary input, load the data
 set into R and make it a data frame called iowa.df.
 
 b. How many rows and columns does iowa.df have?
 
 c. What are the names of the columns of iowa.df?
 
 d. What is the value of row 5, column 7 of iowa.df?
 
 e. Display the second row of iowa.df in its entirety

```{r}
iowa.df <- read.csv("data/iowa.csv",header=T,sep = ";")
iowa.df
```

b.33 rows,10 columns.

c.Year,Rain0,Temp1,Rain1,Temp2,Rain2,Temp3,Rain3,Temp4,Yield.

d.the value of row 5,column 7 of iowa.df is `r iowa.df[5,7]`.

e.
```{r}
iowa.df[2,]
```

## 2

### a. For each of the following commands, either explain why they should be errors, or explain the non-erroneous result.
 vector1 <- c("5", "12", "7", "32")
 max(vector1)
 sort(vector1)
 sum(vector1)
 
 1.vector1是一个由字符"5"  "12" "7"  "32"组成的向量
 
```{r}
vector1 <- c("5", "12", "7", "32")
vector1
```
2.max()函数输出最大值，由于vector1向量中都是字符，字符从左开始比较字符大小，分别比较5,1,7,3.显然最大的是"7"

```{r}
max(vector1)
```
3.sort()函数默认对vector1向量进行递增排序，根据字符大小比较的规则，从小到大依次是"12" "32" "5"  "7" 。

```{r}
sort(vector1)
```
4.出现error,因为vector1向量全是字符类型，无法进行sum().


### b. For the next series of commands, either explain their results, or why they should produce errors.
 vector2 <- c("5",7,12)
 vector2[2] + vector2[3]
 dataframe3 <- data.frame(z1="5",z2=7,z3=12)
 dataframe3[1,2] + dataframe3[1,3]
 list4 <- list(z1="6", z2=42, z3="49", z4=126)
 list4[[2]]+list4[[4]]
 list4[2]+list4[4]
 
1.向量必须包含同一种类型的元素，这里由于同时包含字符和数字类型数据，所以会把数字类型元素变成字符类型元素

```{r}
vector2 <- c("5",7,12)
vector2
```
 会出现error:二进列运算符中有非数值参数.原因是在给vector2赋值时，其第二个和第三个元素都变成了字符类型数据，所以不能进行加运算

2.
```{r}
dataframe3 <- data.frame(z1="5",z2=7,z3=12)
dataframe3
```
```{r}
dataframe3[1,2] + dataframe3[1,3]
```
dataframe3是dataframe类型的数据，它的nrow=1,dataframe3[1,2] =7,dataframe3[1,3]=12，两个数加起来是19.

3.list4是lists类型数据，list4[[2]]和list4[[4]]分别表示list4的第2个和第4个元素，二者都是数字类型，可以进行相加计算.list4[2]和list4[4]分别表示只包含第2个和第4个元素的新list，两个list不能直接进行相加运算。

###  3. Working with functions and operators.

 a. The colon operator will create a sequence of integers in order. It is a special case of the function
 seq() which you saw earlier in this assignment. Using the help command ?seq to learn about
 the function, design an expression that will give you the sequence of numbers from 1 to 10000
 in increments of 372. Design another that will give you a sequence between 1 and 10000 that is
 exactly 50 numbers in length.
```{r}
seq1 <- seq(1,10000,by = 372)
seq1
seq2 <- seq(1,10000,length.out = 50)
seq2
```
 
  b. The function rep() repeats a vector some number of times. Explain the difference between
 rep(1:3, times=3) and rep(1:3, each=3).
```{r}
rep1 <- rep(1:3, times=3)
rep1
rep2 <- rep(1:3, each=3)
rep2
```
 rep(1:3, times=3)表示把1:3一起重复3次，rep(1:3, each=3)表示把1:3分别重复3次.
 
## MB.Ch1.2. 
### The orings data frame gives data on the damage that had occurred in US space shuttle launches prior to the disastrous Challenger launch of 28 January 1986. The observations in rows 1, 2, 4, 11, 13, and 18 were included in the pre-launch charts used in deciding whether to proceed with the launch, while remaining rows were omitted. Create a new data frame by extracting these rows from orings, and plot total incidents against temperature for this new data frame. Obtain a similar plot for the full data set.

```{r}
  library(DAAG)
  orings
  neworings <- orings[c(1,2,4,11,13,18),]
  neworings
  plot(neworings$Total~neworings$Temperature)
  plot(orings$Total~orings$Temperature)
```

##MB.Ch1.4. 
###For the data frame ais (DAAG package)
###(a) Use the function str() to get information on each of the columns. Determine whether any of the columns hold missing values.
###(b) Make a table that shows the numbers of males and females for each different sport. In which sports is there a large imbalance (e.g., by a factor of more than 2:1) in the numbers of the two sexes?


(a).没有缺失值
```{r}
  library(DAAG)
  
  ais
  for(i in 1:13){
    str(ais[,i]) 
  }
  missing_values <- colSums(is.na(ais))
  missing_values
  
```
(b).根据计算，Gym、Netball、T_Sprnt、W_Polo这四项运动男女数量差距比较不平衡.
```{r}
  library(dplyr)
  library(tidyr)
  library(tibble)
  library(DAAG)
  result <- ais |>  group_by(sex) |> count(sport,name = "Count") |>  pivot_wider(names_from = sport, values_from = Count, values_fill = 0) |> column_to_rownames(var = "sex")
  
  print(result)
  tresult <- (t(result))
  tresult <- as.data.frame(tresult)
  tresult
  imbalance <- filter(tresult,(f / m >= 2)|(f / m <=0.5))
  imbalance
```


##MB.Ch1.6.
###Create a data frame called Manitoba.lakes that contains the lake’s elevation (in meters above sea level) and area (in square kilometers) as listed below. Assign the names of the lakes using the row.names() function.
```{r}
  Manitoba.lakes <- data.frame(elevation = c(217,254,248,254,253,227,178,207,217),area = c(24387,5374,4624,2247,1353,1223,1151,755,657) ) 
  row.names(Manitoba.lakes) <-c("Winnipeg","Winnipegosis","Manitoba","SouthernIndian","Cedar","Island","Gods","Cross","Playgreen")
  Manitoba.lakes
```
(a) Use the following code to plot log2(area) versus elevation, adding labeling information (there is an
extreme value of area that makes a logarithmic scale pretty much essential):
```{r}
attach(Manitoba.lakes)
plot(log2(area) ~ elevation, pch=16, xlim=c(170,280))
# NB: Doubling the area increases log2(area) by 1.0
text(log2(area) ~ elevation, labels=row.names(Manitoba.lakes), pos=4)
text(log2(area) ~ elevation, labels=area, pos=2)
title("Manitoba's Largest Lakes")
```

(b) Repeat the plot and associated labeling, now plotting area versus elevation, but specifying ylog=TRUE
in order to obtain a logarithmic y-scale.
```{r}
plot(area ~ elevation, pch=16, xlim=c(170,280), ylog=T)
text(area ~ elevation, labels=row.names(Manitoba.lakes), pos=4, ylog=T)
text(area ~ elevation, labels=area, pos=2, ylog=T)
title("Manitoba's Largest Lakes")
```

##MB.Ch1.7. 
###Look up the help page for the R function dotchart(). Use this function to display the areas ofthe Manitoba lakes (a) on a linear scale, and (b) on a logarithmic scale. Add, in each case, suitable labeling information.

(a).
```{r}
 
  dotchart(log2(area) ,labels = row.names(Manitoba.lakes),pch = 16,main = "Manitoba‘s lakes",xlab ="loig2(area)")

```

(b).
```{r}

  dotchart(area ,labels = row.names(Manitoba.lakes),log = "x",pch = 16,main = "Manitoba‘s lakes",xlab ="area")
```

##MB.Ch1.8. 
###Using the sum() function, obtain a lower bound for the area of Manitoba covered by water.
```{r}
  
   sum(Manitoba.lakes$area)
```


